---
title: "Acumen Code Sample Statistical Programming in R"
author: Carlos López
output: html_notebook
---


<br>

# Creating Martices
```{r}
#HW2 1.1
fun1 <- function(n, miu, sd){
   set.seed(2048);
   matrix_ret <- 0;
   random_dist <- rnorm( n = n, mean = miu, sd = sd);
   if((n %% 2 == 0) & (n %% 3 != 0)){
     
     matrix_ret <- matrix(random_dist, nrow = 2, ncol= n/2, byrow = TRUE)
     
   }
   else if((n %% 2 != 0) & (n %% 3 == 0)){
     matrix_ret <- matrix(random_dist, ncol = 3, ncol = n/3,  byrow = FALSE)
   }
   #if(n %% 2 == 0 & n %% 3 == 0)
   else{
     matrix_ret <- matrix(random_dist, nrow = 6 , ncol = n/6, byrow = TRUE)
   }
   r_val = (dim(matrix_ret)[1])
   c_val = (dim(matrix_ret)[2])
   vector_vals <- apply(matrix_ret, MARGIN = 2, FUN = mean,  na.rm = TRUE)
   for(i in 1:r_val){  
     for(j in 1:c_val){ 
       if(matrix_ret[i, j] < 0){
         return(apply(matrix_ret, MARGIN = 2, FUN = mean,  na.rm = TRUE))
      }
     }
   }
   return(apply(matrix_ret, margin = 2, median,  na.rm = TRUE));
}
   
fun1(50, 0.5, 2)

```
<hr>
# Sorting Mean Values
```{r}
# HW2 Q1.2 

fun2 <- function(list_in){
  len <- length(list_in)
  vec <- lapply(list_in, FUN = mean, na.rm = TRUE)
  len <- length(vec)
  for(i in 2:len){
    val <-  vec[[i]]
    j <- i -1
    
    while(j>=1 && vec[[j]] > val){
      
      vec[j + 1] <- vec[j]
      j = j - 1
      
      
    }
    vec[j + 1] = val
  }
  
    
  return(vec)
}

list_ex = list(c(20, 13, 34, 2), c(2, 3), c(45, 65, 78), c(43, 98, 1, 22), c(3, 5, 10), c(13, 19, 14))

fun2(list_ex)

```
<hr>
# Plotting an Unfair Die
```{r}
# HW1.3 

fun3 <- function(n){
  prob <- c(0.1, 0.3, 0.2, 0.05, 0.3, 0.05)
  vals <- c(1, 2, 3, 4, 5, 6)
  sample_vec <- sample(vals, n, replace = TRUE, prob)
  
  
  hist(sample_vec,
       
       xlab = "Die Number",
       
       ylab = "FREQUENCY",
       
       main = "Histogram of Unfair Die",
       
       breaks = seq(0, 6, 1),
       
       col = "orange",
       
       border = "black",
      
       xlim = c(0, 6),
       ylim = c(0, 55)
  )
  
  
}

fun3(100)
```
<hr>
# Die Comparison
```{r}
#HW 1.4 

fun4 <- function(n){
  fun_sim <-function(v1, v2){
    vals <- c('Die1 > Die2', 'Die1 < Die2', 'Die1 = Die2')
    vec <- c()
      if(v1 > v2){
        vec <- c(vec, vals[1])
      }
      else if(v1 < v2){
        vec <- c(vec, vals[2])
      }
      else{
        
        vec <- c(vec, vals[3])
        
      }
      return(vec)
    }
  die1 <- sample(c(1,2,3,4,5,6), n, replace = TRUE, c(1/6.0, 1/6.0, 1/6.0, 1/6.0, 1/6.0, 1/6.0))
  die2 <- sample(c(1,2,3,4,5,6), n, replace = TRUE, c(1/6.0, 1/6.0, 1/6.0, 1/6.0, 1/6.0, 1/6.0))
  comparison <- mapply(fun_sim, die1, die2)
  return(comparison)
}


fun4(30)
```
<br>
<hr>
<hr>
<br>

# Graphs and Mean Difference Analysis
<br>
#### The average price for stores in the US is shown below

```{r}

data1 <- read.csv(file = "/Users/c-lo/Desktop/STAT2102/carseats.csv", header = T)

function_1 <- function(x){
  
  return(c(Mean = mean(x), Median = median(x)))
  
}
#1
avg_p_us <- mean(subset(data1, US == "Yes")$Price)
avg_p_us
```

#### The average price for rural stores in the US
```{r}
avg_p_nonus <- mean(subset(data1, US == "No")$Price)
avg_p_nonus

```
#### The average price of rural stores in the US
```{r}
avg_p_us_rural <- mean(subset(data1, US == "Yes" & Urban == "No")$Price)
avg_p_us_rural
```
#### The average price of rural stores outside the US

```{r}
avg_p_nonus_rural <- mean(subset(data1, US == "No" & Urban == "No")$Price)
avg_p_nonus_rural
```
#### The store with the maximum price
```{r}
store_max <- subset(data1, Price == max(Price))
store_max
```
#### The store with the minimum price
```{r}
store_min <- subset(data1, Price == min(data1$Price))
store_min
```
#### Shelving Quality Median
```{r}
#3
shelving_med <- tapply(data1$Sales, data1$ShelveLoc, median)
shelving_med
```
#### Median Sales by Shelve Quality and Location
```{r}
rural_urb <- c('Rural', 'Urban')
shelving_med_urban <- tapply(data1$Sales, list(data1$ShelveLoc,rural_urb[as.factor(data1$Urban)]), median)
shelving_med_urban
```
<br>
<br>
```{r}
loc_stat <- c('Outside the US', 'In the US')
propr <- table(data1$US)/nrow(data1)
propc <- table(data1$Age)/nrow(data1)

boxplot(data1$Age ~ loc_stat[as.factor(data1$US)],
        width = prop, height= propc,
        xlab = "Store Location",
        ylab = "AGE",
        main = "Ages for US and Non-US Stores",
        col = c("darkorange", "red"),
        border = c("dodgerblue", "black"),
        notch = T)
```
<hr>

```{r}
propr <- table(data1$ShelveLoc)/nrow(data1)
propc <- table(data1$Age)/nrow(data1)
boxplot(data1$Age ~ data1$ShelveLoc,
        width = propr * 0.5, height = 2.6*propc,
        xlab = "Shelve Quality",
        ylab = "AGE",
        main = "Ages by Shelve Quality",
        col = c("darkorange", "red", "blue"),
        border = c("dodgerblue", "black", "green"), cex = 0.4,
        notch = F)
```
```{r}

barplot(table(data1[, c("ShelveLoc", "Urban")]),
        
        beside = TRUE,
        ylab = "Frequencies",
        
        xlab = "Shelve Quality and Rural/Urban Status",
        
        main = "Disease Status vs Sex",
        
        col = c("blue", "orange", 'red')
)
legend("topleft", legend = unique(as.factor(data1$ShelveLoc)), pch = 15, cex=0.5, col = c("blue", "orange", 'red'))
```

```{r}
fun_conv <- function(x){
  if(x == "No"){
    return("Rural")
  }
  else{
    return("Urban")
  }
}

data1$loc <- mapply(data1$Urban, FUN = fun_conv)
colors <- c("green", "orange")

plot(x = data1$Sales,
     
     y = data1$Price,
     
     xlab = "Sales",
     
     ylab = "Price",
     
     main = "Sales vs Price",
     
     col = colors[unique(as.factor(data1$loc))],
     
     pch = 17,
     
     cex  = 0.5
)


legend("topleft", legend = unique(as.factor(data1$loc)) , pch = 17, cex=0.5, col = colors)
```

```{r}

#8

par(mfrow = c(1,2))

hist(data1$Price, 
     
     xlab = "Price",
     ylab="Frequency",
     main="Price Histogram",
     breaks = seq(0, 195, 5),
     col='blue',
     border='black',
     
)


boxplot(data1$Age ~ data1$US,
        
        xlab = "Store is in the US",
        
        ylab = "AGE",
        main = "Ages for US and Non-US Stores",
        col = c("darkorange", "red"),
        border = c("dodgerblue", "black"),
        notch = T)
```

# Hedge Fund Regression and Hypothesis Test


# Hedge Fund Regression 
```{r}
library(readxl)
hedge <- read_excel('/Users/c-lo/Desktop/metrics_int/HedgeFundMarketData.xlsx')


hedge$ex_market_ret <- hedge$sp_tr - hedge$riskfree

hedge$ex_hedge_ret <- hedge$hedge - hedge$riskfree

#hedge
```


```{r}

library(lmtest)
library(sandwich)

lm_hedge <- lm(ex_hedge_ret ~ ex_market_ret, hedge)
lm_hedge
summary(lm_hedge)
```

```{r}

lm_hedge_s <- coeftest(lm_hedge, vcoc=vcovHC(lm_hedge, type ="HC1"))
lm_hedge_s
# As you see, R^2 and sigma_hat are not included in the new regression output 
# No matter which setting is, heteroskedasticity and homoskedasticity, the R^2 and sigma_hat are the same 
# The t-statistic values of beta_hat are different #
unique(lm_hedge_s)
lm_hedge_s[3]
```

# Testing the Hypothesis

* H_0: the constant is truly zero at the 5% significance 
* H_1: the constant is not truly zero at the 5% significance

```{r}

 lm_hedge_s[5] > 1.965
lm_hedge_s[7] < 0.05
CI_low <- lm_hedge_s[1] - 1.96 * lm_hedge_s[3]
CI_high <- lm_hedge_s[1] + 1.96 * lm_hedge_s[3]
CI <- c(CI_low, CI_high)
CI
```

* As seen above three methods are utilized to determine with certainty that we cannot reject the null hypothesis. First, we fail to reject H_0 because the absolute value of the t-value is less than 1.96, Second, we fail to reject H_0 because the p-value is greater 0.05. Third, we fail to reject H_0 because 0 is within the 95% CI.

### Performing a Robust Regression 

```{r}

mdl <- estimatr::lm_robust(ex_hedge_ret ~ ex_market_ret, data=hedge, se_type="HC1")
summary(mdl)

```

```{r}
0.8283 > 1.96 # t-value < 1.96 
4.100e-01 < 0.05 # p-value > 0.05
0 > -0.00304 & 0 < 0.007373 #95% CI
```

* As seen above three methods are utilized to determine with certainty that we cannot reject the null hypothesis even when we take heteroskedasity into account. 
